---
title: "Using Bayes Rule with Forecasting"
author: "Aditya Mehrotra"
date: "2024-02-14"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      error = TRUE, fig.height = 4)
library(tidyverse)
library(lubridate)
```

## Overview
-- The following document will use R to implement the Bayes Rule with Forecasting on a given Situation

## Situation
Let's assume that Madison, Wisconsin gets about 115 days of precipitation per year. Suppose that when there is precipitation, the forecast on Channel 3000 is correct 93% of the time and when there is no precipitation in the city, they are correct 87% of the time.

## Question 1
### How many days will Channel 3000 correctly forecast in a non-leap year (365 days)

``` {r correct_pred_reg_year}
precipitation_correct_odds = 0.93
nothing_correct_odds = 0.87

precipitation_days = 115
nothing_days = 365 - precipitation_days

correct_forecast = (precipitation_days * precipitation_correct_odds) + (nothing_days * nothing_correct_odds)
round(correct_forecast)
```

#### Math
Correct Forecast = (Odds Correct for Precipitation) * (Days there is Precipitation) + (Odds Correct for Non-Precipitation) * (Days there is No Precipitation)

- Odds Correct for Precipitation = 0.93
- Days there is Precipitation = 115
- Odds Correct for Non-Precipitation = 0.87
- Days there is No Precipitation = 250

Correct Forecast = (0.93) * (115) + (0.87) * (250)

#### Answer
Correct Forecast = 324 Days

## Question 2
### If Channel 3000 predicts precipitation in Madison, what is the likelihood that there is actually precipitation?

```{r channel_3000_precipitation_pred}
forecast_pred_precipitation = ((precipitation_days / 365) * precipitation_correct_odds) + ((nothing_days / 365) * (1 - nothing_correct_odds))

pred_precipitation = ((precipitation_days / 365) * precipitation_correct_odds) / forecast_pred_precipitation

pred_precipitation
```

#### Math
Precipitation Prediction = (((Days of Precipitation) / (Total Days in a Year)) * (Odds of Correct Prediction of Precipitation)) + (((Days of No Precipitation) / (Total Days in a Year)) * (1 - Odds of Correct Prediction of No Precipitation)))

- Days of Precipitation = 115
- Total Days in a Year = 365
- Odds of Correct Prediction of Precipitation = 0.93
- Days of No Precipitation = 365 - Days of Precipitation = 365 - 115 = 250
- (1 - Odds of Correct Prediction of No Precipitation) = (1 - 0.87) = 0.13

Precipitation Prediction = (115/365) * 0.93 + (250/365) * 0.13

#### Bayes Rule
P(Rain|Forecast Rain) = (P(Forecast Rain|Rain) * P(Rain)) / (P(Forecast Rain))

#### Answer
Precipitation Prediction = 76.69%

## Question 3

